---
title: "metaboReports"
subtitle: "`r paste0('v',packageVersion('metaboReports'))`"
author: "Jasen Finch"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  prettydoc::html_pretty:
    toc: true
    highlight: github
    theme: tactile
vignette: >
  %\VignetteIndexEntry{metaboReports-usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(knitr)
library(magrittr)
library(tibble)
```

## Introduction

`metaboReports` provides a simple interface to enable automated, dynamic HTML report generation for results objects created from metabolomics analyses using the powerful R Markdown format.
Detailed information on the R Markdown format can be found [here](https://bookdown.org/yihui/rmarkdown/).

Currently, report methods are available for:

```{r, echo=FALSE,eval=TRUE}
tibble(
  `S4 class` = c('Binalysis','MetaboProfile','Analysis','Assignment','Workflow'),
  Package = c('[binneR](https://github.com/aberHRML/binneR)','[profilePro](https://github.com/jasenfinch/profilePro)','[metabolyseR](https://github.com/jasenfinch/metabolyseR)','[MFassign](https://github.com/jasenfinch/MFassign)','[metaboWorkflows](https://github.com/jasenfinch/metaboWorkflows)')
) %>%
  kable()
```

## Basic usage

First load the library:

```{r setup}
library(metaboReports)
```

The parameters for the report can be defined using the `reportParameters()` function as follows:

```{r parameters}
rp <- reportParameters(title = 'A metabolomics analysis',
                       investigator = 'Steve French',
                       sessionInfo = TRUE,
                       toc = TRUE,
                       path = '.')
```

The report can then be generated for the given object using the following:

```{r report,eval=FALSE}
report(analysis,rp)
```

This will create an output project directory named using the parameter `title` at the specified `path`.
Within this directory, the files necessary to create the report will be generated and include an R Markdown file (`.Rmd`) containing the R and markdown code and a file containing the necessary data (`reportData.rds`).
If `report()` is triggered from within RStudio, an RStudio project (`.proj`) file will also be created.
Once these files are created, `rmarkdown::render()` is automatically called which will generate the final HTML report.
Directories containing cached data and plot image files will also be created during this process.


